R Notebook

### 2018-09-13 article_code.Rmd
comment

```{r}
source("C:/Users/tl3315/Dropbox/coding/cosimulation/co_sim_condi.R")
source("C:/Users/tl3315/Dropbox/coding/cosimulation/cosim_functions.R")
```
```{r}
library(mvtnorm)
library(abind)
```

>>>>

loading the functions, replace with the location of your files
```{r}
source("C:/Users/tl3315/Dropbox/coding/cosimulation/co_sim_condi.R")
source("C:/Users/tl3315/Dropbox/coding/cosimulation/cosim_functions.R")
```
```{r}
library(mvtnorm)
library(abind)
```
